Individual and Differential Harm in Redistricting

### 2022-05-25 paper/paper.Rmd
edit

New Jersey is just one state, and while some of the correlations between measures here are found in other states, some are not.
Appendix \ref{app:corr} calculates these correlations across eight states.
The most consistent correlation is that between our estimate of differential partisan harm and the expected number of seats won by each party, which is usually around 0.98, and always above 0.66 in the eight states we study.

>>>>

New Jersey is just one state, and while some of the correlations between measures here are found in other states, some are not.
Appendix \ref{app:corr} shows these correlations across simulated plans in eight states.
The most consistent correlation is between estimated differential partisan harm and the expected number of seats won by each party, which is usually around 0.98, and always above 0.66 in the eight states we study.
